TacticToe: Learning the Game of Tactics

### 2018-01-20 tactictoe_jv.tex
search: wip

@@

@@

@@

@@

\[Policy(a_i) = \frac{1 + Visit(a_i))}{\sqrt{Visit(a_i))}}\]

The exploitation function $Exploitation$ is the average of the evaluation of 
all nodes descendant of $a_i$ in the current search tree.

@@

\subsection{End of the proof search}
The proof search stops when one of these 3 conditions is realized:
\item It found a proof (i.e. the root node is solved). In this case, 
the search returns a minimized and 
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It has saturated. 
There is no more tactics to be applied to any open goal. (todo: define open 
goal somewhere).

\item It exceeded a given time limit.

@@

\begin{align*}
E_{none} (a_i) &= 0 \\
E_{productive} (a_i) &= 1\\
E_r (a_i) &= \frac{card\ Positive(r,a_i)}{r}\\
\end{align*}

For all evaluations functions, if a tactic is not productive then there is no 
output to evaluate, so the result is a failure and a reward of $0$ will be 
backpropagated.

>>>>

Since there is a bijection between tactics of the tree search 
and the node they 
produced, any function define on tactics of the tree search can be map to a 
function defined on nodes.

@@

The estimation through the distance produced by the tactic selectors are hard 
to translate into a prior tactic policy, so we rely only on the order of 
tactics to estimate the probability with which a tactic should be tried.
Let $t_0,\ldots,t_500$ be the list of preselected tactics ordered by their 
distance to a goal $g$. Let $c_policy$ be a constant heuristic that estimates 
how likely a tactic $t_i$ is to prove the goal compared to the rest of the 
tactics $t_{i+1},\ldots,t_500$. We make the strong assumption that $c_policy$ 
is constant across the search. We can now calculate the prior policy by:

\[PriorPolicy(t_{i}) = (1 - c_policy)^{i} * c_policy\]

The first term of the multiplication is the probability that none of the better 
ranked tactic is selected.

In fact, these probabilities are never used directly and only serves as a 
guidance to our deterministic node selection algorithm over many simulations.

@@

\begin{align*}
PriorEvaluation_{none} (a_i) &= 0 \\
PriorEvaluation_{productive} (a_i) &= 1\\
PriorEvaluation_r (a_i) &= \frac{card\ Positive(r,a_i)}{r}\\
\end{align*}

For all evaluations functions, if a tactic is not productive then there is no 
output to evaluate, so the result is a failure and a reward of $0$ will be 
given for this node. The same thing happens if the node selected is already 
proven or a descendant of a proven goal. 
Experimentally, it is preferable not to 
filter proven (or descendants of proven) nodes before 
node selection to keep the estimation of the algorithm balanced.

@@

The exploration term is determined by the prior policy and the current policy 
where as the exploitation is exactly the current evaluation build from prior of 
evaluations of descendants of $a_i$.

@@

\[Policy(a_i) = \frac{1 + Visit(a_i))}{\sqrt{Visit(p))}}\]
The policy is approximatively the  percentage of time a node was visited.The 
square root skews this probability to favor even more exploration of nodes with 
few visits.

The exploitation function $Exploitation$ is the average of the evaluation of 
all nodes descendant of $a_i$ (itself included) in the current search tree.   
\[Exploitation{a_i} = Average_{b \in Desc(a_i))} {PriorEvaluation(b)}\]

@@

\subsection{End of the proof search}
The proof search stops when one of these 3 conditions is realized:
\begin{itemize}
\item It found a proof (i.e. the root node is solved). In this case, 
the search returns a minimized and 
prettified proof script (see Section~\ref{sec:proofdisplay}).
\item It has saturated. 
There is no more tactics to be applied to any open goal. \todo{define open 
goal}
\item It exceeded a given time limit.
\end{itemize}

@@
